---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mean.calculations

<!-- badges: start -->
```last_change_badge(2020-11-18)```
```licensebadge(MIT)```
<!-- badges: end -->

The goal of mean.calculations is to provide the `mean_differences` function for STAT545b.

## Installation

You can install the released version of mean.calculations from Github with:

``` r
devtools::install_github("sunj9195/mean.calculations")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mean.calculations)
mean_differences(6:8, 3:5)
```

## Development Explaination

This R package includes the mean_differences function in Assignment 1-B. 

1. loaded in console
```library(devtools), install_package("purrr")```

2. The package is initially built in owner's local folders with the function ```create_package()```, and ```use_git()``` to create package and git repo. 

3. mean_differences function has been wrote and documented with ```use_r("mean_difference")```. 

4. ```devtools::document()``` is being used throughout the development to document the changes. 

5. ```load_all()``` is being used throughout the development to load the changes. 

6. ```check()``` is being used throughout the development to see if there is any errors. 

7. mit license added with ```use_mit_license(“Sandra Sun”)```. 

8. Description file has been updated manually. 

9. Added roxygen skeleton to document the details of function. Para, return, export, etc. has beenn updated to give user a better understanding. 

10. ```Install & restart``` s being used throughout the development.

11. ```test```
  * ```use_testthat()``` to create local test folder
  * ```use_test("mean_difference")``` to create test .R file
  * wrote test functions with expect_x functions
12. ```REAEME``` to create READ file
  * ```use_readme_rmd()```
  * ```devtools::install_github("sunj9195/mean_differences")```
  * ```build_readme()```
13. ```vignette``` to create detailed explanation file for the function
  * ```use_vignette()```
  * ```build_vignettes()```
14. Link to github
  * created new repository in github
  * link local to github
15. Install packages with ```install_github()```

## Code of Conduct
  
Please note that the mean.calculations project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.










