---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mean.calculations

<!-- badges: start -->
<!-- badges: end -->

The goal of mean.calculations is to provide the `mean_differences` function for STAT545b.

Use `mean_differences` to:

* Calculate the differences in two means. 

__Note:__ This package is still in its infancy. There are many other critical features to come.

## Design Choices

`mean_differences`:
* Calculate the differences in means for numeric vector.

## Basic Usage and Examples

`library(mean.calculations)`

Function to calculate for differences in two arithmetic means.

```{r}
mean.calculations::mean_differences(c(6, 8, 10), c(4, 6, 8))
```

```{r}
mean.calculations::mean_differences(6:20, 5:15)
```


## Installation

`mean_differences` is not on CRAN yet, so the best way to install it is:

``` r
devtools::install_github("sunj9195/mean.calculations")
```

## Development Explaination

This R package includes the mean_differences function in Assignment 1-B. 

1. loaded in console
`library(devtools), install_packages("purrr")`

2. The package is initially built in owner's local folders with the function `create_package()`, and `use_git()` to create package and git repo. 

3. mean_differences function has been wrote and documented with `use_r("mean_difference")`. 

4. `devtools::document()` is being used throughout the development to document the changes. 

5. `load_all()` is being used throughout the development to load the changes. 

6. `check()` is being used throughout the development to see if there is any errors. 

7. mit license added with `use_mit_license(“Sandra Sun”)`. 

8. Description file has been updated manually. 

9. Added roxygen skeleton to document the details of function. Para, return, export, etc. has been updated to give user a better understanding. 

10. `Install & restart` s being used throughout the development.

11. `test`
  * `use_testthat()` to create local test folder
  * `use_test("mean_difference")` to create test .R file
  * wrote test functions with expect_x functions
12. `REAEME` to create READ file
  * `use_readme_rmd()`
  * `devtools::install_github("sunj9195/mean.calculations")`
  * `build_readme()`
13. `vignette` to create detailed explanation file for the function
  * `use_vignette()`
  * `build_vignettes()`
14. Link to github
  * created new repository in github
  * link local to github
15. Install packages with `install_github()`

## Code of Conduct
  
Please note that the mean.calculations project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
